New first figure

### 2021-05-17 manuscript/bef_stability/appendixB.Rmd
Update metaweb figures

knitr::opts_chunk$set(
  cache = TRUE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE
)

@@

Heterogeneity in the fishing date may introduce variability due to different
climatic or environmental conditions but also to the life cycle of the species.
For instance, early surveys may precede the egg hatching and youngs-of-the-year.
In order to reduce heterogeneity in the sampling date, only one sampling per
year was retained if there were more in a given year, the one that had the most
species and then the most individuals. Finally, most of the fish sampling
occurred in September (Median: mid-August). There was low heterogeneity of the
sampling month within stations, with the median sampling month being mid-August
where the median standard deviation of the sampling month was  month, i.e. three
weeks. To further reduce sampling heterogeneity, we only kept the sampling in
which the length of stream sampled along the stream was inside the median length
sampled more or less 30%.

@@

Diet information was obtained from fishbase.org and literature (Appendix A,
Table S2). The diet information contained from two to three life stages by
species, the life stages being defined by the body size of the fishes. Over the
57 fish species, only 7 had a piscivorous life stage and only three had a strict
piscivorous life stage. Fish species were then largely omnivorous.

@@

trophic_building_caption <- paste0( "Define trophic species and trophic
  interactions. (1) Each
  species is divided into 9 body size classes. We gathered data about
  the food diet of each fish species and how food diet varies according to
  ontogeny. (2) The life stage of a trophic species is determined by the
  median of the body size class, hereafter midpoint. A trophic link is set between the trophic
  species and the resources associated to this life stage. (3) For piscivorous
  trophic species, the trophic links among fishes are defined according to
  the predator/prey body size ratio. The predation window of a trophic
  species ranges from 3% to 45% of its midpoint. A trophic
  link is set between the predator trophic species and every trophic species whose
  midpoint of body size class range was included in the predation window.")

@@

The life stage to which a trophic species belongs was determined by the median
of the body size range of the trophic species, each life stage being delimited
by a body size range. In return, this trophic species has trophic interactions
with the resource nodes of its life stage. The trophic interactions between a
predator and a prey were determined by the predator-prey body size ratio
[@brose_predator_2019; @poisot_structure_2016; @schneider_body_2012]. For a
given trophic species, we first determined if its body size range overlapped
with a piscivorous life stage (Fig. \@ref(fig:p-net-inf)). If the trophic
species was piscivorous, we determined its prey size range from 3% to 45% of the
median of its size range. A trophic interaction was set for each trophic species
whose corresponding size class median felt into the prey range of the predator
trophic species (Fig. \@ref(fig:p-net-inf)). To sum up, the metaweb contains
feeding interactions (1) between trophic species, (2) between trophic species
and resource nodes and (3) between resource nodes.

@@

The local food-webs (i.e. one network by
sampling) were obtained by determining the trophic species of each fish
individual in the community. According to the trophic species present in a given
community, we set the trophic interactions between them as defined in the metaweb. 
All the resource nodes were assumed to be present in each local network.
Thus, the structure of the local food-webs varied according to the presence of
the trophic species.

@@

We used stream spatial network methods to interpolate water temperature, water
flow and BOD. Indeed, stream characteristics make interpolation more
complicated than in terrestrial areas. Interpolations in terrestrial areas are
often based on euclidean distance, which is not possible for streams as two
streams can be close but disconnected. For those reason, we used stream spatial
network methods to interpolate water temperature, water flow and BOD.

@@

The performance of the interpolations was evaluated with leave one out
cross-validation (already implemented in the SSN package), i.e. the value of the
interpolated variable of each station was predicted after removing it from the
dataset.

@@

The CV of biomass over time can cover multiple temporal dynamics, including
increases, decreases, no trends or and a mixture of the above. Theoretically, however, the CV
computed to quantify stability is often represented with the assumption that the
overall dynamic of the biomass varies around an equilibrium
[@kefi_advancing_2019]. In order to approach the condition of equilibrium, we
kept only the stations that show no clear temporal trends. To characterise the
biomass temporal dynamics according to their trajectories, we used the symbolic
aggregated approximation method (SAX), which is commonly used in time series
analysis and implemented in the `jmotif` R package [@senin_grammarviz_2018].
This method classifies time series rather than quantifies trends. Therefore, it
is generic enough to encompass a diversity of temporal trajectories. The
classification necessitates three steps. The time series are first normalized.
Then, the dimensionality of the time series is reduced by a Piecewise
Aggregation Approximation (PAA) method. Each time series is divided into $N$
frames of equal size that allows to reduce the dimensionality of the time
series. For each frame, we simply kept the mean value of the time series.  The
final stage is to qualify each frame into string. Because values of normalized
time series typically follow a normal distribution ($N(0,1)$), a breakpoint can
be computed by dividing the area under the normal distribution in equal parts.
The algorithm attributes an alphabetic letter to each part from the lowest to
the highest ($a$, $b$, $c$, ...). We set three breakpoints, so $a$, $b$ and $c$.
Finally, the trajectory of each time series is classified as a combination of
$a$, $b$, $c$ letters. $abc$ and $cba$ time series represent respectively
monotonic increasing and decreasing trajectories. For data analysis, we kept
only the $bbb$ which represent time series that showed no temporal tendencies,
with respect to our methodology.

@@

\begin{table}
\caption{\label{tab:hyp-sem} Presentation of the links 
of the Structural Equation Models associated with the references supporting the links.}
\begin{center}
\begin{tabular}{ m{7cm}| m{1cm}| m{6cm}}
    \hline
    Link & Sign & References\\
    \hline
    PCA1 Avg stream size $\to$ Species richness & (+) & Galiana et al. (2018) \\
    \hline
    PCA2 Avg temperature $\to$ Species richness & (+/-) & Woods et al. (2020); Gauzens et al. (2020) \\
    \hline
    PCA1 Avg stream size $\to$ Connectance & (-) & Galiana et al. (2018) \\
    \hline
    PCA2 Avg temperature $\to$ Connectance & (+/-) & O’Gorman et al. (2019);
    Oksanen et al. (1981)\\
    \hline
    Species richness $\to$ Connectance & (-) & Winemiller (1989); Dunne (2006) \\
    \hline
    PCA1 Avg stream size $\to$ Avg trophic level & (+) & Post et al. (2000); Doi et al. (2009); McHugh et al. (2010) \\
    \hline
    PCA2 Avg temperature $\to$ Avg trophic level & (+/-) & O’Gorman et al. (2017)\\
    \hline
    Species richness $\to$ Avg trophic level & (+) & Schneider et al. (2016)\\
    \hline
    Species richness $\to$ Synchrony & (-) & Thébault and Loreau (2005); Loreau and de Mazancourt (2008); Thibaut and Connolly (2013) \\
    \hline
    Connectance $\to$ Synchrony & (+) & Thébault and Loreau (2005)\\
    \hline
    Avg trophic level $\to$ Synchrony & (+) & Raimondo et al. (2004); McCann and Rooney (2009) \\
    \hline
    PCA1 Avg stream size $\to$ Synchrony & (-) & Wang et al. (2019)\\
    \hline
    PCA2 Avg temperature $\to$ Synchrony & (?) & \\
    \hline
    Species richness $\to$ CVsp & (+) & Jiang et al. (2009)\\
    \hline
    Connectance $\to$ CVsp & (+) & Thébault and Loreau (2005)\\
    \hline
    Avg trophic level $\to$ CVsp & (-) & McCann and Rooney (2009); Shanafelt and Loreau (2018)\\
    \hline
    PCA1 Avg stream size $\to$ CVsp & (?) & \\
    \hline
    PCA2 Avg temperature $\to$ CVsp & (+) & Kratina et al. (2012); Fussmann et al. (2014)\\
    \hline
    CVsp $\to$ Biomass stability & (-) & Thibaut and Connolly (2013)\\
    \hline
    Synchrony $\to$ Biomass stability & (-) & Thibaut and Connolly (2013)\\
    \hline
    Species richness $\to$ Total biomass & (+) & Schneider et al. (2016)\\
    \hline
    Connectance $\to$ Total biomass & (+/-) & Thébault and Loreau (2003); Poisot
    et al. (2013)\\
    \hline
    Avg trophic level $\to$ Total biomass & (+) & Wang and Brose (2018)\\
    \hline
    PCA1 Avg stream size $\to$ Total biomass & (+) & Post et al. (2000); Allan and Ibanez Castillo (2009); Doi et al. (2009)\\
    \hline
    PCA2 Avg temperature $\to$ Total biomass & (+/-) & Kratina et al. (2012);
    Tabi et al. (2019)\\
    \hline
    \end{tabular}
\end{center}
\end{table}

@@

)
format_coef_table(stab_sem_rich) %>%
  select(-Crit.Value) %>%
  mutate_if(is.numeric, round, digits = 2) %>%
  mutate(Std.Estimate = cell_spec(Std.Estimate, bold = ifelse(P.Value <= 0.05,
	T, F), format = "latex", escape = F)
    ) %>%
kable(
  format = "latex",
  booktabs = T,
  caption = est_stab_sem_caption,
  escape = F,
  digits = 2
  ) %>%
collapse_rows(columns = 1, valign = "top") %>%
kable_styling(latex_options = c("striped", "scale_down"))
```

@@

format_coef_table(bm_sem_rich) %>%
  select(-Crit.Value) %>%
  mutate_if(is.numeric, round, digits = 2) %>%
  mutate(Std.Estimate = cell_spec(Std.Estimate, bold = ifelse(P.Value <= 0.05, T, F))) %>%
kable(
  format = "latex",
  booktabs = T,
  caption = est_bm_sem_caption,
  escape = F, 
  digits = 2
  ) %>%
collapse_rows(columns = 1, valign = "top") %>%
kable_styling(latex_options = c("striped", "scale_down"))
```

@@

```{r, fig.height = 7.5, fig.cap = sens_cap}
p_sens_bm <- plot_sensivity_analysis(
  .data = sem_bm_results,
  inverse_label_order = TRUE) +
  labs(x = "", title = "Median of annual community biomass") +
  theme(legend.position = "none", plot.margin = unit(c(0, 0, 0, 28), units = "mm"))

p_sens_stab <- plot_sensivity_analysis(.data = sem_stab_results,
  inverse_label_order = TRUE) +
  labs(title = "Temporal stability of annual community biomass") +
  guides(color = guide_legend(direction = "horizontal", nrow = 2))
legend_b <- get_legend(p_sens_stab)
p_sens_stab %<>% + theme(legend.position = "none", plot.margin = unit(c(0,0,0,27), units = "mm"))
p <- plot_grid(
  p_sens_bm, p_sens_stab, legend_b, nrow = 3,
  rel_heights = c(1, 1, .12)
  #,
  #labels = c("Total biomass", "Biomass stability")
)
p
```

>>>>

knitr::opts_chunk$set(
  cache = TRUE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.align = "center",
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE
)

@@

Heterogeneity in the fishing date may introduce variability due to different
climatic or environmental conditions but also to the life cycle of the species.
For instance, early surveys may precede the egg hatching and youngs-of-the-year.
In order to reduce heterogeneity in the sampling date, only one sampling per
year was retained if there were more in a given year, the one that had the most
species and then the most individuals. Finally, most of the fish sampling
occurred in September (Median: mid-August). There was low heterogeneity of the
sampling month within stations, with the median sampling month being mid-August
where the median standard deviation of the sampling month was 0.7 month, i.e. three
weeks. To further reduce sampling heterogeneity, we only kept the sampling in
which the length of stream sampled along the stream was inside the median length
sampled more or less 30%.

@@

Diet information was obtained from fishbase.org and literature (Appendix A,
Table S2). The diet information described two to three life stages by
species, the life stages being defined by the body size of the fishes. Over the
57 fish species, only 7 had a piscivorous life stage and only three had a strict
piscivorous life stage. Fish species were then largely omnivorous.

@@

trophic_building_caption <- paste0( "Definition of trophic species and trophic
  interactions. (1) Each
  species is divided into 9 body size classes. We gathered data about
  the food diet of each fish species and how food diet varies according to
  ontogeny. (2) The life stage of a trophic species is determined by the
  median of the body size class, hereafter midpoint. A trophic link is set between the trophic
  species and the resources associated to this life stage. (3) For piscivorous
  trophic species, the trophic links among fishes are defined according to
  the predator/prey body size ratio. The predation window of a trophic
  species ranges from 3% to 45% of its midpoint. A trophic
  link is set between the predator trophic species and every trophic species whose
  midpoint of body size class range was included in the predation window.")

@@

The life stage to which a trophic species belongs was determined by the median
of the body size range of the trophic species, each life stage being delimited
by a body size range. In return, this trophic species has trophic interactions
with the resource nodes of its life stage. The trophic interactions between a
predator and a prey were determined by the predator-prey body size ratio
[@brose_predator_2019; @poisot_structure_2016; @schneider_body_2012]. For a
given trophic species, we first determined if its body size range overlapped
with a piscivorous life stage (Fig. \@ref(fig:p-net-inf)). If the trophic
species was piscivorous, we determined its prey size range from 3% to 45% of the
median of its size range. A trophic interaction was set for each trophic species
whose corresponding size class median felt into the prey range of the predator
trophic species (Fig. \@ref(fig:p-net-inf)). To sum up, the metaweb contains
feeding interactions (1) among trophic species, (2) among trophic species
and resource nodes and (3) among resource nodes.

@@

The local food-webs (i.e. networks at each sampling event) were obtained by
determining the trophic species of each fish individual in the community.
According to the trophic species present in a given community, we set the
trophic interactions between them as defined in the metaweb.  All the resource
nodes were assumed to be present in each local network.  Thus, the structure of
the local food-webs varied according to the presence of the trophic species.

@@

We used stream spatial network methods to interpolate water temperature, water
flow and BOD at the sampling sites. Indeed, stream characteristics make interpolation more
complicated than in terrestrial areas. Interpolations in terrestrial areas are
often based on euclidean distance, which is not possible for streams as two
streams can be close but disconnected. For those reason, we used stream spatial
network methods to interpolate water temperature, water flow and BOD.

@@

The performance of the interpolations was evaluated with leave one out
cross-validation (already implemented in the SSN package), i.e. the value of the
interpolated variable of each station was predicted after removing it from the
dataset (Table S3).

@@

The CV of biomass over time can cover multiple temporal dynamics, including
increases, decreases, no trends or and a mixture of the above. Theoretically, however, the CV
computed to quantify stability is often represented with the assumption that the
overall dynamic of the biomass varies around an equilibrium
[@kefi_advancing_2019]. In order to approach the condition of equilibrium, we
kept only the stations that show no clear temporal trends. To characterise the
biomass temporal dynamics according to their trajectories, we used the symbolic
aggregated approximation method (SAX), which is commonly used in time series
analysis and implemented in the `jmotif` R package [@senin_grammarviz_2018].
This method classifies time series rather than quantifies trends. Therefore, it
is generic enough to encompass a diversity of temporal trajectories. The
classification necessitates three steps. The time series are first centred such
as the mean value is equal to 0.
Then, the dimensionality of the time series is reduced by a Piecewise
Aggregation Approximation (PAA) method. Each time series is divided into $N$
frames of equal size that allows to reduce the dimensionality of the time
series. For each frame, we simply kept the mean value of the time series.  The
final stage is to qualify each frame into string. Because values of normalized
time series typically follow a normal distribution ($N(0,1)$), a breakpoint can
be computed by dividing the area under the normal distribution in equal parts.
The algorithm attributes an alphabetic letter to each part from the lowest to
the highest ($a$, $b$, $c$, ...). We set two breakpoints, thereby simplifying
our time series into three periods.
Finally, the trajectory of each time series is classified as a combination of
$a$, $b$, $c$ letters. $abc$ and $cba$ time series represent respectively
monotonic increasing and decreasing trajectories. For data analysis, we kept
only the $bbb$ which represent time series that showed no temporal tendencies,
with respect to our methodology.

@@

\begin{table}
\caption{\label{tab:hyp-sem} Presentation of the hypothesis underlying the
effects included in the Structural Equation Models with supporting references.}
\begin{center}
\begin{tabular}{ m{7cm}| m{1cm}| m{6cm}}
    \hline
    Link & Sign & References\\
    \hline
    PCA1 Avg stream size $\to$ Species richness & (+) & Galiana et al. (2018) \\
    \hline
    PCA2 Avg temperature $\to$ Species richness & (+/-) & Woods et al. (2020); Gauzens et al. (2020) \\
    \hline
    PCA1 Avg stream size $\to$ Connectance & (-) & Galiana et al. (2018) \\
    \hline
    PCA2 Avg temperature $\to$ Connectance & (+/-) & O’Gorman et al. (2019);
    Oksanen et al. (1981)\\
    \hline
    Species richness $\to$ Connectance & (-) & Winemiller (1989); Dunne (2006) \\
    \hline
    PCA1 Avg stream size $\to$ Avg trophic level & (+) & Post et al. (2000); Doi et al. (2009); McHugh et al. (2010) \\
    \hline
    PCA2 Avg temperature $\to$ Avg trophic level & (+/-) & O’Gorman et al. (2017)\\
    \hline
    Species richness $\to$ Avg trophic level & (+) & Schneider et al. (2016)\\
    \hline
    Species richness $\to$ Synchrony & (-) & Thébault and Loreau (2005); Loreau and de Mazancourt (2008); Thibaut and Connolly (2013) \\
    \hline
    Connectance $\to$ Synchrony & (+) & Thébault and Loreau (2005)\\
    \hline
    Avg trophic level $\to$ Synchrony & (+) & Raimondo et al. (2004); McCann and Rooney (2009) \\
    \hline
    PCA1 Avg stream size $\to$ Synchrony & (-) & Wang et al. (2019)\\
    \hline
    PCA2 Avg temperature $\to$ Synchrony & (?) & \\
    \hline
    Species richness $\to$ CVsp & (+) & Jiang et al. (2009)\\
    \hline
    Connectance $\to$ CVsp & (+) & Thébault and Loreau (2005)\\
    \hline
    Avg trophic level $\to$ CVsp & (-) & McCann and Rooney (2009); Shanafelt and Loreau (2018)\\
    \hline
    PCA1 Avg stream size $\to$ CVsp & (?) & \\
    \hline
    PCA2 Avg temperature $\to$ CVsp & (+) & Kratina et al. (2012); Fussmann et al. (2014)\\
    \hline
    CVsp $\to$ Biomass stability & (-) & Thibaut and Connolly (2013)\\
    \hline
    Synchrony $\to$ Biomass stability & (-) & Thibaut and Connolly (2013)\\
    \hline
    Species richness $\to$ Total biomass & (+) & Schneider et al. (2016)\\
    \hline
    Connectance $\to$ Total biomass & (+/-) & Thébault and Loreau (2003); Poisot
    et al. (2013)\\
    \hline
    Avg trophic level $\to$ Total biomass & (+) & Wang and Brose (2018)\\
    \hline
    PCA1 Avg stream size $\to$ Total biomass & (+) & Post et al. (2000); Allan and Ibanez Castillo (2009); Doi et al. (2009)\\
    \hline
    PCA2 Avg temperature $\to$ Total biomass & (+/-) & Kratina et al. (2012);
    Tabi et al. (2019)\\
    \hline
    \end{tabular}
\end{center}
\end{table}

@@

)
format_coef_table(stab_sem_rich) %>%
  select(-Crit.Value) %>%
  mutate_if(is.numeric, round, digits = 2) %>%
  mutate(Std.Estimate = cell_spec(Std.Estimate, bold = ifelse(P.Value <= 0.05,
	T, F), format = "latex", escape = F)
    ) %>%
kable(
  format = "latex",
  booktabs = T,
  align = "c",
  caption = est_stab_sem_caption,
  escape = F,
  digits = 2
  ) %>%
collapse_rows(columns = 1, valign = "top") %>%
kable_styling(latex_options = c("striped", "scale_down"))
```

@@

format_coef_table(bm_sem_rich) %>%
  select(-Crit.Value) %>%
  mutate_if(is.numeric, round, digits = 2) %>%
  mutate(Std.Estimate = cell_spec(Std.Estimate, bold = ifelse(P.Value <= 0.05, T, F))) %>%
kable(
  format = "latex",
  booktabs = T,
  align = "c",
  caption = est_bm_sem_caption,
  escape = F, 
  digits = 2
  ) %>%
collapse_rows(columns = 1, valign = "top") %>%
kable_styling(latex_options = c("striped", "scale_down"))
```

@@

```{r, fig.height = 7.5, fig.cap = sens_cap}
p_sens_bm <- plot_sensivity_analysis(
  .data = sem_bm_results,
  inverse_label_order = TRUE) +
  geom_hline(yintercept = 0) +
  labs(x = "", title = "Median of annual community biomass") +
  theme(legend.position = "none", plot.margin = unit(c(0, 0, 0, 28), units = "mm"))

p_sens_stab <- plot_sensivity_analysis(.data = sem_stab_results,
  inverse_label_order = TRUE) +
  geom_hline(yintercept = 0) +
  labs(title = "Temporal stability of annual community biomass") +
  guides(color = guide_legend(direction = "horizontal", nrow = 2))
legend_b <- get_legend(p_sens_stab)
p_sens_stab %<>% + theme(legend.position = "none", plot.margin = unit(c(0,0,0,27), units = "mm"))
p <- plot_grid(
  p_sens_bm, p_sens_stab, legend_b, nrow = 3,
  rel_heights = c(1, 1, .12)
  #,
  #labels = c("Total biomass", "Biomass stability")
)
p
```

### 2021-05-17 manuscript/bef_stability/fig1_biomass_network.Rmd
Add BOD to SEM figures + change correlation in review
Update metaweb figures

@@

>>>>

png(
  filename = mypath("manuscript", "bef_stability", "figs", "metaweb2.png"), 
  units = "in",
  width = 5,
  height = 7,
  pointsize = 12*96/72,
  res = 200 
)
org_par <- par(
  mar = c(4, 0, 0, 0) + 0,
  oma = c(0, 0, 0, 0),
  xpd = NA 
)
PlotWeb(
  TL = TL,
  webTL = metaweb_analysis$metaweb,
  colnode = rgb(t(col2rgb(sp_color[node_sp]))/255,alpha=0.7),
  abund = 6,
  collink=rgb(t(col2rgb("grey50"))/255,alpha=0.05),
  scale_abun = .01
)

@@

dev.off()
par(org_par)
